A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-02-27 analysis/paper/paper.Rmd
bump paper + pdf generation

```{r}
add_sfig(
figure_file("methods_timeline.svg", "4-method_characterisation"),
"methods_over_time", 
"New TI methods over time. **a** Number of methods published or in preprint. **b** Number of methods which can handle a particular type of trajectory."
)
```

@@

`r anchor("fig", "evaluation_overview")`
![](`r figure_file("ti_evaluation_overview_v2.svg", experiment_id="evaluation_overview")`)
`r ref("fig", "evaluation_overview")` Overview of the evaluation

@@

`r anchor("fig", "implementation_overview")`
![](`r figure_file("implementation_overview.svg", experiment_id="4-method_characterisation")`)
`r ref("fig", "implementation_overview", anchor=TRUE)` First characterization of each method.

@@

```{r}
add_sfig(
figure_file("qc_over_time.svg","4-method_characterisation"), 
"qc_over_time", 
"Quality control scores and number of citations over time"
)
```

@@

```{r}
add_sfig(
figure_file("method_components.svg","4-method_characterisation"), 
"method_components", 
"TI methods frequently share steps"
)
```
## Evaluating the accuracy of the inferred trajectory

@@

```{r}
add_sfig({
        figure_file('wrapping.svg', '4-method_characterisation')
}, 
"wrapping", 
"Our wrapping workflow", 
15, 
7.5
)
```

@@

```{r}
add_sfig(
figure_file("trajectory_type_trees.svg","2-dataset_characterisation/2-trajectory_types"), 
"trajectory_type_tree", 
"Different trajectory types can be classified in a directed acyclic graph, in which certain types are a generalisation of other trajectory types.", 
15, 
10
)
```

@@

```{r}
add_sfig({
figure_file("edge_flip_comparison.svg", experiment_id="3-score_rules/4-edge_flip")
}, 
"edge_flip_comparison", 
"Edge flip score values for common trajectory topologies", 
15, 
5
)
```

>>>>

```{r}
add_sfig(
figure_file("methods_timeline.pdf", "4-method_characterisation"),
"methods_over_time", 
"New TI methods over time. **a** Number of methods published or in preprint. **b** Number of methods which can handle a particular type of trajectory."
)
```

@@

`r anchor("fig", "evaluation_overview")`
![](`r figure_file("ti_evaluation_overview_v2.pdf", experiment_id="evaluation_overview")`)
`r ref("fig", "evaluation_overview")` Overview of the evaluation

@@

`r anchor("fig", "implementation_overview")`
![](`r figure_file("implementation_overview.pdf", experiment_id="4-method_characterisation")`)
`r ref("fig", "implementation_overview", anchor=TRUE)` First characterization of each method.

@@

```{r}
add_sfig(
figure_file("qc_over_time.pdf","4-method_characterisation"), 
"qc_over_time", 
"Quality control scores and number of citations over time"
)
```

@@

```{r}
add_sfig(
figure_file("method_components.pdf","4-method_characterisation"), 
"method_components", 
"TI methods frequently share steps"
)
```
## Evaluating the accuracy of the inferred trajectory

@@

```{r}
add_sfig({
        figure_file('wrapping.pdf', '4-method_characterisation')
}, 
"wrapping", 
"Our wrapping workflow", 
15, 
7.5
)
```

@@

```{r}
add_sfig(
figure_file("trajectory_type_trees.pdf","2-dataset_characterisation/2-trajectory_types"), 
"trajectory_type_tree", 
"Different trajectory types can be classified in a directed acyclic graph, in which certain types are a generalisation of other trajectory types.", 
15, 
10
)
```

@@

```{r}
add_sfig({
figure_file("edge_flip_comparison.pdf", experiment_id="3-score_rules/4-edge_flip")
}, 
"edge_flip_comparison", 
"Edge flip score values for common trajectory topologies", 
15, 
5
)
```
